---
title: | 
        <center> SUPPLEMENTARY MATERIALS </center>
author:  ""
output:
  pdf_document: 
    toc: yes
    toc_depth: 5
    latex_engine: lualatex
  html_document: 
    toc: yes
    toc_depth: 5
  word_document: default
---

```{r setup, include=FALSE}
remove(list = ls())
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
library(readr)
library(metafor)
library(tidyr)
library(kableExtra)
library(MAd)
library(dplyr)
```

\newpage

```{r}
df <- read_csv("df.csv")
df_info<-read.csv("df_info.csv")

# Effect sizes
#Note: TD group has been used as $X_1$ and ASD group as $X_2$

df <- escalc(measure="SMD",
       m1i=C_Mean, 
       m2i=ASD_Mean, 
       sd1i=C_Sd, 
       sd2i=ASD_Sd, 
       n1i=c_n, 
       n2i=asd_n,
       data=df, 
       drop00=TRUE, 
       vtype="AV", #computes the sampling variances with the usual large-sample approximation but plugging the sample-size weighted average of the Hedges' g values into the equation
       var.names=c("yi","vi","SMD"), add.measure=TRUE,
       append=TRUE, replace=TRUE)
```

# Meta-analyses with r = .30

```{r}
df_agg<-MAd::agg(data=df, id=id, es=yi, var=vi, method = 'BHHR', cor = .30) 
```

## Dataset

Effect sizes (Hedge's *g*) and varinaces for each of the included studies, with *r* = .30

```{r}
names(df_info)[names(df_info) == "Authors"] <-  "authors" 
names(df_info)[names(df_info) == "es"] <-  "Hedge's g" 
df_agg<-merge.data.frame(df_info[,c(1,2)], df_agg, by="id")
```

```{r}
kbl(df_agg, digits = 2, col.names = c("ID", "Authors", "Hedge's g", "Var")) %>%
  kable_paper() %>%
  kableExtra::kable_styling(latex_options = "hold_position")
```


## Descriptive statistics

```{r}
info<- Reduce(function(x,y) merge(x,y,by="id",all=TRUE) ,list(df_agg[,-2],df_info))
info<-info[,c("id","authors","country",
              "c_n","c_m_f_ratio","c_age_range","c_age_m","c_age_sd",
              "asd_n","asd_m_f_ratio","asd_age_range","asd_age_m","asd_age_sd",
              "synch_type","es", "var")]
df_agg<-info[,c(1,2,14,15,16)]

names(info)[names(info) == "id"] <-  "ID"
names(info)[names(info) == "authors"] <-  "Authors"
names(info)[names(info) == "country"] <-  "Country"
names(info)[names(info) == "synch_type"] <-  "Type of Synchrony"
names(info)[names(info) == "c_n"] <-  "N"
names(info)[names(info) == "c_m_f_ratio"] <-  "M/F ratio" #td
names(info)[names(info) == "c_age_range"] <-  "range" #td
names(info)[names(info) == "c_age_m"] <-  "mean" #td
names(info)[names(info) == "c_age_sd"] <-  "sd" #td
names(info)[names(info) == "asd_n"] <-  "N" #asd
names(info)[names(info) == "asd_m_f_ratio"] <-  "M/F ratio" #asd
names(info)[names(info) == "asd_age_range"] <-  "range" #asd
names(info)[names(info) == "asd_age_m"] <-  "mean" #asd
names(info)[names(info) == "asd_age_sd"] <-  "sd" #asd
names(info)[names(info) == "es"] <-  "Hedge's g" 
```

 
```{r}
kbl(info, digits = 2) %>%
  kable_paper() %>%
  add_header_above(c(" "= 3, " " = 2, "Age" = 3, " " = 2, "Age" = 3, " " = 3)) %>%
  add_header_above(c(" " = 3, "TD Group" = 5, "ASD Group" = 5, " " = 3)) %>%
  kableExtra::kable_styling(latex_options="scale_down")  %>%
  kableExtra::kable_styling(latex_options = "hold_position")
```


## Random-effects meta-analysis

### Models

```{r, echo=TRUE}
m.random <- rma(yi=es, vi=var, data=df_agg, method="REML")
RE.results <- summary(m.random)
print(RE.results)
```

 
```{r, echo=TRUE}
#fit moderation model (type of synchrony)
moderation.random <- rma(yi=es, vi=var, mods = ~ synch_type, data=df_agg, method="REML")
summary(moderation.random)
```

### Forest plot

Dotted line is the prediction interval

```{r}
forest(m.random, # combined effect size
       annotate=TRUE,
       df_agg$var, # variance of the composite hp .5
       showweights=T,
       header=T,
       slab=df_agg$authors,
       ilab=df_agg$synch_type,
       ilab.xpos = -5,
       ilab.pos = 4, 
       cex=.75,
       xlim=c(-10,11),
       xlab="Hedge's g", 
       addpred = TRUE)
text(-3.8, 15, "SynchType", cex=.75, font=2)

### add text with Q-value, dfs, p-value, and I^2 statistic
text(-10, -1.8, pos=4, cex=0.70, 
     bquote(paste("(Q = ", .(formatC(m.random$QE, digits=2, format="f")),
     ", df = ", .(m.random$k - m.random$p),
     ", p < .0001", "; ", 
     I^2, " = ", .(formatC(m.random$I2, digits=2, format="f")), "%; ", 
     tau, " = ", .(formatC(sqrt(m.random$tau2), digits=2, format="f")) , ")" )))
```

### Prediction interval

```{r}
predict(m.random)

#metafor::predict.rma(m.random)
```

### Funnel plot (trim-and-fill method)

```{r, fig.align="center"}
### carry out trim-and-fill analysis
taf<-trimfill(m.random,main="", 
                ma.fixed = FALSE, fixed = FALSE, random = TRUE, label=F)

### draw funnel plot with missing studies filled in
funnel(taf, legend=TRUE, xlab="Hedge's g")
```

### Model corrected for publication bias (trim-and-fill method)

```{r}
summary(trimfill(m.random))
```


### Sensitivity analyses

#### Leave-One-Out

```{r}
sens.random<-as.data.frame(leave1out(m.random))

sens.random<-data.frame(df_agg$authors, format(round(sens.random[,],2),nsmal=2))
sens.random$CI<-paste0("[",sens.random$ci.lb,";",sens.random$ci.ub,"]")
sens.random$tau<-sqrt(as.numeric(sens.random$tau2))
sens.random$tau2<-NULL
sens.random<-sens.random[,c(1:2,10,13,12)]
sens.random[,1]<-as.character(sens.random[,1])
names(sens.random)[names(sens.random) == "df_agg.authors"] <- "Authors"
names(sens.random)[names(sens.random) == "estimate"] <- "Estimate"



# Compute prediction intervals using leave-one-out method

PI.random <- data.frame(Authors = character(), 
                            #CI = character(),  
                            PI = character())

for (j in 1:nrow(df_agg)) {
    df_agg_l1o <- df_agg[-j, ]  # Remove one study from the dataset
    
    m.leave1out.random <- rma(yi = es, vi = var, data = df_agg_l1o, method = "REML")  # Run model
    
    predicted <- predict(m.leave1out.random, interval = "prediction")  # Compute prediction interval
    
    # conf_lb<-round(predicted$ci.lb, digits = 2)
    # conf_ub<-round(predicted$ci.ub, digits = 2)
    pred_lb<-round(predicted$pi.lb, digits = 2)
    pred_ub<-round(predicted$pi.ub, digits = 2)
  
    
    # Create a new row with results
    new_row <- data.frame(Authors = df_agg$authors[j], 
                          #CI = paste0("[",conf_lb,";",conf_ub,"]"), 
                          PI = paste0("[",pred_lb,";",pred_ub,"]"))
    
    # Bind the new row to results_table
    PI.random <- rbind(PI.random, new_row)
}

sens.random<-merge(sens.random, PI.random, by="Authors", all=TRUE)

kbl(sens.random, digits = 2) %>%
  kable_paper()  %>%
  kableExtra::kable_styling(latex_options = "hold_position")

```

#### Cook's distance

```{r, fig.align="center"}
dinf<-influence(m.random)
highest<-max(dinf$inf$cook.d)
plot(dinf$inf$cook.d, ylab = "Cook's distance", xlab = "ID", col=ifelse(dinf$inf$cook.d==highest, "red", "black"), pch=ifelse(dinf$inf$cook.d==highest, 19, 1), type = "b")
axis(1, at=dinf$inf$slab, labels=dinf$inf$slab)
```

Note that study IDs follow alphabetical order of included studies and their specifications reported in the descriptive statistic's table

```{r}
ES_3 <- predict(m.random)$pred
I2_3 <- m.random$I2
tau_3 <- sqrt(m.random$tau2)
CI_3 <- paste0("[",round((predict(m.random)$ci.lb), digits = 2),
               ";",round((predict(m.random)$ci.ub), digits = 2),"]")
PI_3 <- paste0("[",round((predict(m.random)$pi.lb), digits = 2),
               ";",round((predict(m.random)$pi.ub), digits = 2),"]")
```

\newpage

# Meta-analyses with r = .50

```{r}
df_agg<-MAd::agg(data=df, id=id, es=yi, var=vi, method = 'BHHR', cor = .50) 
```

## Dataset

Effect sizes (Hedge's *g*) and varinaces for each of the included studies, with *r* = .50

```{r}
names(df_info)[names(df_info) == "Authors"] <-  "authors" 
df_agg<-merge.data.frame(df_info[,c(1,2)], df_agg, by="id")
```

```{r}
kbl(df_agg, digits = 2, col.names = c("ID", "Authors", "Hedge's g", "Var")) %>%
  kable_paper() %>%
  kableExtra::kable_styling(latex_options = "hold_position")
```


## Descriptive statistics

```{r}
info<- Reduce(function(x,y) merge(x,y,by="id",all=TRUE) ,list(df_agg[,-2],df_info))
info<-info[,c("id","authors","country",
              "c_n","c_m_f_ratio","c_age_range","c_age_m","c_age_sd",
              "asd_n","asd_m_f_ratio","asd_age_range","asd_age_m","asd_age_sd",
              "synch_type","es", "var")]
df_agg<-info[,c(1,2,14,15,16)]

names(info)[names(info) == "id"] <-  "ID"
names(info)[names(info) == "authors"] <-  "Authors"
names(info)[names(info) == "country"] <-  "Country"
names(info)[names(info) == "synch_type"] <-  "Type of Synchrony"
names(info)[names(info) == "c_n"] <-  "N"
names(info)[names(info) == "c_m_f_ratio"] <-  "M/F ratio" #td
names(info)[names(info) == "c_age_range"] <-  "range" #td
names(info)[names(info) == "c_age_m"] <-  "mean" #td
names(info)[names(info) == "c_age_sd"] <-  "sd" #td
names(info)[names(info) == "asd_n"] <-  "N" #asd
names(info)[names(info) == "asd_m_f_ratio"] <-  "M/F ratio" #asd
names(info)[names(info) == "asd_age_range"] <-  "range" #asd
names(info)[names(info) == "asd_age_m"] <-  "mean" #asd
names(info)[names(info) == "asd_age_sd"] <-  "sd" #asd
names(info)[names(info) == "es"] <-  "Hedge's g" 
```

 
```{r}
kbl(info, digits = 2) %>%
  kable_paper() %>%
  add_header_above(c(" "= 3, " " = 2, "Age" = 3, " " = 2, "Age" = 3, " " = 3)) %>%
  add_header_above(c(" " = 3, "TD Group" = 5, "ASD Group" = 5, " " = 3)) %>%
  kableExtra::kable_styling(latex_options="scale_down")  %>%
  kableExtra::kable_styling(latex_options = "hold_position")
```



## Random-effects meta-analysis


### Models

```{r, echo=TRUE}
m.random <- rma(yi=es, vi=var, data=df_agg, method="REML")
RE.results <- summary(m.random)
print(RE.results)
```

 
```{r, echo=TRUE}
#fit moderation model (type of synchrony)
moderation.random <- rma(yi=es, vi=var, mods = ~ synch_type, data=df_agg, method="REML")
summary(moderation.random)
```

### Forest plot

Dotted line is the prediction interval

```{r}
forest(m.random, # combined effect size
       annotate=TRUE,
       df_agg$var, # variance of the composite hp .5
       showweights=T,
       header=T,
       slab=df_agg$authors,
       ilab=df_agg$synch_type,
       ilab.xpos = -5,
       ilab.pos = 4, 
       cex=.75,
       xlim=c(-10,11),
       xlab="Hedge's g", 
       addpred = TRUE)
text(-3.8, 15, "SynchType", cex=.75, font=2)

### add text with Q-value, dfs, p-value, and I^2 statistic
text(-10, -1.8, pos=4, cex=0.70, 
     bquote(paste("(Q = ", .(formatC(m.random$QE, digits=2, format="f")),
     ", df = ", .(m.random$k - m.random$p),
     ", p < .0001", "; ", 
     I^2, " = ", .(formatC(m.random$I2, digits=2, format="f")), "%; ", 
     tau, " = ", .(formatC(sqrt(m.random$tau2), digits=2, format="f")) , ")" )))
```
### Prediction interval

```{r}
predict(m.random)

#metafor::predict.rma(m.random)
```

### Funnel plot (trim-and-fill method)

```{r, fig.align="center"}
### carry out trim-and-fill analysis
taf<-trimfill(m.random,main="", 
                ma.fixed = FALSE, fixed = FALSE, random = TRUE, label=F)

### draw funnel plot with missing studies filled in
funnel(taf, legend=TRUE, xlab="Hedge's g")
```

### Model corrected for publication bias (trim-and-fill method)

```{r}
summary(trimfill(m.random))
```


### Sensitivity analyses

#### Leave-One-Out

```{r}
sens.random<-as.data.frame(leave1out(m.random))

sens.random<-data.frame(df_agg$authors, format(round(sens.random[,],2),nsmal=2))
sens.random$CI<-paste0("[",sens.random$ci.lb,";",sens.random$ci.ub,"]")
sens.random$tau<-sqrt(as.numeric(sens.random$tau2))
sens.random$tau2<-NULL
sens.random<-sens.random[,c(1:2,10,13,12)]
sens.random[,1]<-as.character(sens.random[,1])
names(sens.random)[names(sens.random) == "df_agg.authors"] <- "Authors"
names(sens.random)[names(sens.random) == "estimate"] <- "Estimate"



# Compute prediction intervals using leave-one-out method

PI.random <- data.frame(Authors = character(), 
                            #CI = character(),  
                            PI = character())

for (j in 1:nrow(df_agg)) {
    df_agg_l1o <- df_agg[-j, ]  # Remove one study from the dataset
    
    m.leave1out.random <- rma(yi = es, vi = var, data = df_agg_l1o, method = "REML")  # Run model
    
    predicted <- predict(m.leave1out.random, interval = "prediction")  # Compute prediction interval
    
    # conf_lb<-round(predicted$ci.lb, digits = 2)
    # conf_ub<-round(predicted$ci.ub, digits = 2)
    pred_lb<-round(predicted$pi.lb, digits = 2)
    pred_ub<-round(predicted$pi.ub, digits = 2)
  
    
    # Create a new row with results
    new_row <- data.frame(Authors = df_agg$authors[j], 
                          #CI = paste0("[",conf_lb,";",conf_ub,"]"), 
                          PI = paste0("[",pred_lb,";",pred_ub,"]"))
    
    # Bind the new row to results_table
    PI.random <- rbind(PI.random, new_row)
}

sens.random<-merge(sens.random, PI.random, by="Authors", all=TRUE)

kbl(sens.random, digits = 2) %>%
  kable_paper()  %>%
  kableExtra::kable_styling(latex_options = "hold_position")

```

#### Cook's distance

```{r, fig.align="center"}
dinf<-influence(m.random)
highest<-max(dinf$inf$cook.d)
plot(dinf$inf$cook.d, ylab = "Cook's distance", xlab = "ID", col=ifelse(dinf$inf$cook.d==highest, "red", "black"), pch=ifelse(dinf$inf$cook.d==highest, 19, 1), type = "b")
axis(1, at=dinf$inf$slab, labels=dinf$inf$slab)
```

Note that study IDs follow alphabetical order of included studies and their specifications reported in the descriptive statistic's table

```{r}
ES_5 <- predict(m.random)$pred
I2_5 <- m.random$I2
tau_5 <- sqrt(m.random$tau2)
CI_5 <- paste0("[",round((predict(m.random)$ci.lb), digits = 2),
               ";",round((predict(m.random)$ci.ub), digits = 2),"]")
PI_5 <- paste0("[",round((predict(m.random)$pi.lb), digits = 2),
               ";",round((predict(m.random)$pi.ub), digits = 2),"]")
```


\newpage

# Meta-analyses with r = .70

```{r}
df_agg<-MAd::agg(data=df, id=id, es=yi, var=vi, method = 'BHHR', cor = .70) 
```

## Dataset

Effect sizes (Hedge's *g*) and varinaces for each of the included studies, with *r* = .70

```{r}
names(df_info)[names(df_info) == "Authors"] <-  "authors" 
df_agg<-merge.data.frame(df_info[,c(1,2)], df_agg, by="id")
kbl(df_agg, digits = 2, col.names = c("ID", "Authors", "Hedge's g", "Var")) %>%
  kable_paper() %>%
  kableExtra::kable_styling(latex_options = "hold_position")
```

## Descriptive statistics

```{r}
info<- Reduce(function(x,y) merge(x,y,by="id",all=TRUE) ,list(df_agg[,-2],df_info))
info<-info[,c("id","authors","country",
              "c_n","c_m_f_ratio","c_age_range","c_age_m","c_age_sd",
              "asd_n","asd_m_f_ratio","asd_age_range","asd_age_m","asd_age_sd",
              "synch_type","es", "var")]
df_agg<-info[,c(1,2,14,15,16)]

names(info)[names(info) == "id"] <-  "ID"
names(info)[names(info) == "authors"] <-  "Authors" 
names(info)[names(info) == "country"] <-  "Country"
names(info)[names(info) == "synch_type"] <-  "Type of Synchrony"
names(info)[names(info) == "c_n"] <-  "N"
names(info)[names(info) == "c_m_f_ratio"] <-  "M/F ratio" #td
names(info)[names(info) == "c_age_range"] <-  "range" #td
names(info)[names(info) == "c_age_m"] <-  "mean" #td
names(info)[names(info) == "c_age_sd"] <-  "sd" #td
names(info)[names(info) == "asd_n"] <-  "N" #asd
names(info)[names(info) == "asd_m_f_ratio"] <-  "M/F ratio" #asd
names(info)[names(info) == "asd_age_range"] <-  "range" #asd
names(info)[names(info) == "asd_age_m"] <-  "mean" #asd
names(info)[names(info) == "asd_age_sd"] <-  "sd" #asd
names(info)[names(info) == "es"] <-  "Hedge's g" 


kbl(info, digits = 2) %>%
  kable_paper() %>%
  add_header_above(c(" "= 3, " " = 2, "Age" = 3, " " = 2, "Age" = 3, " " = 3)) %>%
  add_header_above(c(" " = 3, "TD Group" = 5, "ASD Group" = 5, " " = 3)) %>%
  kableExtra::kable_styling(latex_options="scale_down") %>%
  kableExtra::kable_styling(latex_options = "hold_position")

```


## Random-effects meta-analysis

### Models

```{r, echo=TRUE}
m.random <- rma(yi=es, vi=var, data=df_agg, method="REML")
RE.results <- summary(m.random)
print(RE.results)
```

 
```{r, echo=TRUE}
#fit moderation model (type of synchrony)
moderation.random <- rma(yi=es, vi=var, mods = ~ synch_type, data=df_agg, method="REML")
summary(moderation.random)
```

### Forest plot

Dotted line is the prediction interval

```{r}
forest(m.random, # combined effect size
       annotate=TRUE,
       df_agg$var, # variance of the composite hp .5
       showweights=T,
       header=T,
       slab=df_agg$authors,
       ilab=df_agg$synch_type,
       ilab.xpos = -5,
       ilab.pos = 4, 
       cex=.75,
       xlim=c(-10,11),
       xlab="Hedge's g", 
       addpred = TRUE)
text(-3.8, 15, "SynchType", cex=.75, font=2)

### add text with Q-value, dfs, p-value, and I^2 statistic
text(-10, -1.8, pos=4, cex=0.70, 
     bquote(paste("(Q = ", .(formatC(m.random$QE, digits=2, format="f")),
     ", df = ", .(m.random$k - m.random$p),
     ", p < .0001", "; ", 
     I^2, " = ", .(formatC(m.random$I2, digits=2, format="f")), "%; ", 
     tau, " = ", .(formatC(sqrt(m.random$tau2), digits=2, format="f")) , ")" )))
```

### Prediction interval

```{r}
predict(m.random)

#metafor::predict.rma(m.random)
```

### Funnel plot (trim-and-fill method)

```{r, fig.align="center"}
### carry out trim-and-fill analysis
taf<-trimfill(m.random,main="", 
                ma.fixed = FALSE, fixed = FALSE, random = TRUE, label=F)

### draw funnel plot with missing studies filled in
funnel(taf, legend=TRUE, xlab="Hedge's g")
```


### Model corrected for publication bias (trim-and-fill method)
```{r}
summary(trimfill(m.random))
```


### Sensitivity analyses

#### Leave-One-Out

```{r}
sens.random<-as.data.frame(leave1out(m.random))

sens.random<-data.frame(df_agg$authors, format(round(sens.random[,],2),nsmal=2))
sens.random$CI<-paste0("[",sens.random$ci.lb,";",sens.random$ci.ub,"]")
sens.random$tau<-sqrt(as.numeric(sens.random$tau2))
sens.random$tau2<-NULL
sens.random<-sens.random[,c(1:2,10,13,12)]
sens.random[,1]<-as.character(sens.random[,1])
names(sens.random)[names(sens.random) == "df_agg.authors"] <- "Authors"
names(sens.random)[names(sens.random) == "estimate"] <- "Estimate"



# Compute prediction intervals using leave-one-out method

PI.random <- data.frame(Authors = character(), 
                            #CI = character(),  
                            PI = character())

for (j in 1:nrow(df_agg)) {
    df_agg_l1o <- df_agg[-j, ]  # Remove one study from the dataset
    
    m.leave1out.random <- rma(yi = es, vi = var, data = df_agg_l1o, method = "REML")  # Run model
    
    predicted <- predict(m.leave1out.random, interval = "prediction")  # Compute prediction interval
    
    # conf_lb<-round(predicted$ci.lb, digits = 2)
    # conf_ub<-round(predicted$ci.ub, digits = 2)
    pred_lb<-round(predicted$pi.lb, digits = 2)
    pred_ub<-round(predicted$pi.ub, digits = 2)
  
    
    # Create a new row with results
    new_row <- data.frame(Authors = df_agg$authors[j], 
                          #CI = paste0("[",conf_lb,";",conf_ub,"]"), 
                          PI = paste0("[",pred_lb,";",pred_ub,"]"))
    
    # Bind the new row to results_table
    PI.random <- rbind(PI.random, new_row)
}

sens.random<-merge(sens.random, PI.random, by="Authors", all=TRUE)

kbl(sens.random, digits = 2) %>%
  kable_paper() %>%
  kableExtra::kable_styling(latex_options = "hold_position")
```

#### Cook's distance

```{r, fig.align="center"}
dinf<-influence(m.random)
highest<-max(dinf$inf$cook.d)
plot(dinf$inf$cook.d, ylab = "Cook's distance", xlab = "ID", col=ifelse(dinf$inf$cook.d==highest, "red", "black"), pch=ifelse(dinf$inf$cook.d==highest, 19, 1), type = "b")
axis(1, at=dinf$inf$slab, labels=dinf$inf$slab)
```


Note that study IDs follow alphabetical order of included studies and their specifications reported in the descriptive statistic's table

```{r}
ES_7 <- predict(m.random)$pred
I2_7 <- m.random$I2
tau_7 <- sqrt(m.random$tau2)
CI_7 <- paste0("[",round((predict(m.random)$ci.lb), digits = 2),
               ";",round((predict(m.random)$ci.ub), digits = 2),"]")
PI_7 <- paste0("[",round((predict(m.random)$pi.lb), digits = 2),
               ";",round((predict(m.random)$pi.ub), digits = 2),"]")
```


# Comparing results 

```{r}
comparison <- data.frame(
  Correlation = c("r = .30", "r = .50", "r = .70"),
  ES = c(ES_3, ES_5, ES_7),
  I2 = c(I2_3, I2_5, I2_7),
  tau = c(tau_3, tau_5, tau_7),
  CI = c(CI_3, CI_5, CI_7),
  PI = c(PI_3, PI_5, PI_7)
)

kbl(comparison, digits = 2, caption = "Results of the three meta-analyses with different hypothesized correlations") %>%
  kable_paper() %>%
  kableExtra::kable_styling(latex_options = "hold_position")
```

